\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-24 draft.tex
Slight language modifications in Footnote 2 (nested loops)

Some reducers use two (or more) top-level loops to compute the output, possibly
interleaved with some non-looping code. These loops are executed
sequentially, repeatedly iterating over the input list from its beginning. For
example, for calculating the standard deviation, one first computes the average
of inputs and then uses it to compute the final result (using two passes over
the input list). In that case, we suggest to verify the reducer by first
partitioning it into two (or more) reducers, each containing a single top-level
loop, and then verifying these reducers separately.
\footnote{Nested
loops can be removed by adding additional branch statements, since both the inner and outer loop are over the same input list.
In fact, such program construct never occured in examples we have ever seen.} The top-level
loops communicate through shared variables.  After the transformation, reducers
corresponding to the second top-level loop (and possibly further such loops)
will work with random initial values of the shared variable, which over-approximates the original behavior. Usually, the second (or further) top-level loop are commutative even with arbitary initial shared variable values and hence J-ReCoVer can be used to prove it.

>>>>

Some reducers use two (or more) top-level loops to compute the output, possibly
interleaved with some non-looping code. These loops are executed sequentially,
repeatedly iterating over the input list from its beginning. For example, for
calculating the standard deviation, one first computes the average of inputs and
then uses it to compute the final result (using two passes over the input list).
In that case, we suggest to verify the reducer by first partitioning it into two
(or more) reducers, each containing a single top-level loop, and then verifying
these reducers separately.\footnote{Nested loops can be removed by adding
additional branch statements since both the inner and outer loop are over the
same input list. In fact, such a program construct has never occurred in the
examples we have seen.} The top-level loops communicate through shared
variables. After the transformation, reducers corresponding to the second
top-level loop (and possibly further such loops) will work with random initial
values of the shared variable, which over-approximates the original behavior.
Usually, the second (or further) top-level loop are commutative even with
arbitrary initial shared variable values and hence J-ReCoVer can be used to
prove it.
